% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[overlapped]{res}
\usepackage[hidelinks]{hyperref}
\usepackage{hyphenat}
\usepackage{array}
\usepackage{textcomp}
% the margin option causes section titles to appear to the left of body text
%\textwidth=5.7in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (get helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\raggedright  % Prefer uneven right hand side over hyphenation

\newcommand{\experience}[5]{
    \textbf{#3}, #4 \hfill #1 -- #2 \\
    #5
}

\newcommand{\education}[4]{
    \textbf{#2}, #3 \hfill #1 \\
    #4
}

\begin{document}

\name{Miriam Zimmerman}

\address{
  \href{mailto:miriam@mutexlox.com}{miriam@mutexlox.com} \\
  \hfill \href{https://www.linkedin.com/in/miriam-zimmerman-9a2507117}{www.linkedin.com/in/miriam-zimmerman-9a2507117} \\
}
\address{  % The \hfills are to right-align the lines
  \hfill \href{https://mutexlox.com}{https://mutexlox.com} \\
  \hfill Boston, Massachusetts
}

\begin{resume}

% \section{Interests} Kernel and other low-level programming and security (primarily binary exploitation, reverse engineering, and cryptography)

\section{Summary}
  Senior software engineer with extensive experience in C++, C, and Python and
  strong experience with Go and Rust, and experience as a technical lead for
  small teams of engineers. Skilled at taking a problem from problem
  statement to design to implementation, even when design and implementation
  can span years and take multiple engineers.

\section{Experience}
  \vspace{0.5ex}

  \experience{2022}{current}{Google: Senior Software Engineer}{ChromeOS Telemetry}{
    \begin{itemize} \itemsep -1pt
        \item Tech Lead for ChromeOS A/B Experimentation, taking ownership of
          testing improvements, providing technical guidance for formal process
          documents, and working with managers and other engineers to
          coordinate priorities and track project timelines.
        \item Leading implementation for a multi-year, multi-engineer project
          that enables early-boot A/B experimentation for platform code:
          \vspace{-0.5em}
          \begin{itemize} \itemsep -1pt
              \item Conduct client outreach with project manager to ensure
                design meets user needs.
              \item Project expected to unblock 5+ teams, allowing safer, more
                data-driven decisions org-wide, e.g. better analysis of
                performance impacts of memory management changes.
          \end{itemize}
        \item Mentor junior engineers to help them improve their skills,
          delegating well-scoped work to them and providing appropriate
          guidance, including by writing detailed design documents for broadly
          scoped problems that break down the problems into suitable pieces.
        \item Review roughly 10 code changes per week, unblocking numerous
          clients and ensuring that they launch experiments safely without
          regressing key ``guardrail'' metrics.
        \item Awards: Silver Q3 2023 company-wide Healthy award, Q4 2023
          honorable mention for ChromeOS Execution Excellence Emmy, and 15 peer
          and spot bonuses since late 2022.
    \end{itemize}}

  \experience{2018}{2022}{Google: Software Engineer}{ChromeOS Telemetry}{
    \begin{itemize} \itemsep -1pt
        \item Designed, planned, and assigned work for early-boot A/B
          experimentation, ensuring safe, automated disaster recovery.
       \item Designed and implemented late-boot platform A/B experimentation,
         working with clients to assess requirements. Used by dozens of
         experiments, enabling safer, more data-driven platform changes.
        \item Established integration tests for crash reporter, eliminating many
          bugs and preventing large classes of regressions.
        \item Implemented actionable alerts to enable dozens of teams to easily
          track specific crash types over time and increase their awareness of
          new ones.
        \item Improved reliability of crash reporter by adding metrics, fixing
          bugs, and reducing server load that was causing high-severity crashes
          to be lost.
    \end{itemize}
  }

  \experience{2015}{2018}{Google: Software Engineer}{Cloud Security}{
    \begin{itemize} \itemsep -1pt
        \item Exceeded key enterprise customer requirements by implementing
          a virtual Trusted Platform Module, enabling key secure boot workflows
          for all customers of Google Cloud.
        \item Increased difficulty for attackers that escape a VM to move
          laterally to other machines, improving Google's security posture
          against malicious actors.
        \item Evaluated several options for detecting Spectre and Meltdown
          attacks, including their false positive and negative rates, and
          produced a report on detection options.
        \item Designed, implemented, and evaluated methods of using x86
          performance counters to detect specific malicious behavior patterns,
          culminating in a well-researched request to Intel for CPU behavior
          changes that were eventually implemented and released in future
          hardware generations.
        \item Automated testing for an experimental Type-I hypervisor used for
          secure cloud computing, reducing time to test from 30 minutes to 5.
        \item Collaborated with a Cloud Security director to finalize an
          inclusion plan that I wrote for the organization.
    \end{itemize}
  }

  \experience{2017}{2021}{Volunteer Teacher}{Advanced Placement CS A, Kelso High School}{
    \begin{itemize} \itemsep -1pt
      \item Co-taught an AP CS class to high school students in an
        underfunded public school, as part of Microsoft's Technology Education
        and Learning Support program.
      \item Trained the professional classroom teacher until she was
        comfortable teaching the class on her own, establishing a sustainable
        CS curriculum there.
    \end{itemize}
  }

\section{Education}
  \vspace{0.5ex}

  \education{2015}{Carnegie Mellon University}{School of Computer Science}
  {B.S. in Computer Science with University Honors}

\section{Languages}
  C++, C, Python, Go, bash, Rust, x86 assembly, Java, SQL, JavaScript, SML

\section{Tools}
  vim, gdb, bazel, googletest, Abseil C++ libs, protobuf, git, Mercurial, svn, Eclipse

\end{resume}
\end{document}

